IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-04-23 response.tex

\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}

\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}
\newcounter{response}[reviewer]
\setcounter{response}{0}

\let\svbibcite\bibcite
\def\bibcite#1#2{\svbibcite{#1}{R#2}}
\makeatletter
\let\svbiblabel\@biblabel
\def\@biblabel#1{\svbiblabel{R#1}}
\makeatother

\renewcommand{\theequation}
	{E\arabic{equation}}

\renewcommand{\thefigure}
	{F\arabic{figure}}

\renewcommand{\thetable}
	{T\arabic{table}}

@@

\newenvironment{response}
	{\refstepcounter{response} \medskip \noindent \textbf{Response:}\ }
	{\medskip}

\begin{document}
	\includepdf{letter.pdf}

	\begin{reviewer}
		\begin{point}
			This paper assumed that the perfect channel state information (CSI) of the whole system is available at the base station. However, since the IRS is in general not equipped with a radio frequency chain, the accurate CSI of the reflecting links established by the IRS is very challenging to obtain. The reviewer wonders if the proposed algorithm can also be applied to a case where the imperfect CSI of the network is available at the base station.
			\label{pt:1.1}
		\end{point}

		\begin{response}
			Thank you for pointing out the CSI acquisition issue regarding the cascaded link. The proposed passive beamforming algorithms rely on such cascaded CSIT, and recent researches proposed element-wise on/off switching \cite{M-Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020} techniques to solve this issue. Those references have been cited in the literature review. To address the comment, we have revised the simulation results and applied the proposed algorithms to an imperfect CSIT model where the estimation of the cascaded link at subband $n$ is
			\begin{equation}
				\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
			\end{equation}
			where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d. CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$. Simulation result in Fig.~\ref{fi:re_csi} demonstrates the robustness of the proposed passive beamforming algorithm to cascaded CSIT inaccuracy for broadband SWIPT with different number of IRS elements.

@@

			\begin{figure}[!h]
				\centering
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_csi.tex}
				}
				\caption{Average R-E region with imperfect cascaded CSIT for $M=1$, $N=16$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
				\label{fi:re_csi}
			\end{figure}

			\label{re:1.1}
		\end{response}

		\begin{point}
			This paper considered a relatively simple system model where there is only one user in the system. However, in practice, there can be many users co-existing in the SWIPT systems and there may also be two different and independent quality of service requirements: energy harvesting requirement and information decoding requirement. It could be better if the authors can clarify if the proposed algorithm can be employed in a more general case where the base station and the IRS cooperate to serve multiple users in the same time slot.
			\label{pt:1.2}
		\end{point}

		\begin{response}
			Multi-user IRS-aided SWIPT is very interesting and should be investigated in the future, but is left for future work for the ``don't run before we can walk'' reasons explained below:

@@

			\emph{First}, it is important to remind the reviewer that the problem of joint waveform and beamforming design for a multi-user SWIPT system without IRS has never been studied in the literature. In other words, it would be premature at this stage to address this multiuser IRS-aided SWIPT since the underlying building block of multiuser SWIPT is not known. Only once the problem of multiuser joint waveform and beamforming for multi-user SWIPT has been addressed, can we investigate the multiuser joint waveform and beamforming design for IRS-aided SWIPT. Those problems could be addressed in future research, but are not the scope of this paper.

			\emph{Second}, the emphasis is on single-user because we believe a proper understanding of the single-user case is crucial before jumping into multi-user scenarios. Our modeling of SWIPT is not "simple": not only we transmit both information and power, we deal with joint space and frequency optimization through a joint beamforming and waveform problem that is challenging due to the nonlinearity of the rectifier that induces coupling among frequencies components. This completely contrasts with any existing IRS-aided SWIPT work as discussed in the introduction \cite{M-Wu2020b,M-Tang2019,M-Wu2020a}. To reflect this aspect, we have revised the title to ``IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model''.

			\emph{Third}, multi-user WPT leads to its own set of challenges compared single-user WPT. Taking an non-IRS-aided WPT, frequency and spatial domains can be decoupled in single-user case, while they cannot be decoupled in the multi-user case, as shown in \cite{M-Clerckx2016a,M-Huang2017}. Consequently, single-user and multi-user WPT are designed differently in \cite{M-Clerckx2016a,M-Huang2017}. Though the SWIPT case has not been studied, the same set of problems is expected to occur between single user and multiuser case and would be even more challenging since communication is delivered simultaneously with power. Adding IRS into the picture would make it even more complicated.
			\label{re:1.2}
		\end{response}

@@

		\begin{point}
			It is well known that after employing semidefinite programming for handling the phase shift matrix at the IRS, it is very unlikely to obtain a rank-one phase shift matrix without any further modification. The reviewer notices that the authors proposed the Gaussian randomization method to ensure a rank-one solution. Also, the convergence of the proposed overall algorithm also relies on the unit-rank solution. Therefore, to make this paper more comprehensive and convincing, it is suggested to provide more results (such as figures, tables, and data analysis) in the simulation part to show that the rank-one solution can always be obtained even without applying the Gaussian randomization. As this is a very important and interesting conclusion to the colleagues working in the same area, it could be better if the authors can further discuss, interpret, and clarify this in a remark.
			\label{pt:1.3}
		\end{point}

		\begin{response}
			Thank you for raising this issue. To prove the rank-\num{1} property of the IRS matrix $\boldsymbol{\Phi}$, we notice that for any feasible $\boldsymbol{\Phi}$ to problem~\eqref{M-op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds due to the modulus constraint~\eqref{M-co:irs_modulus}. Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{M-ob:irs} and formulate an equivalent problem as
			\begin{maxi!}
				{\boldsymbol{\Phi}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_equivalent_rate}
				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_equivalent_modulus}
				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_equivalent_sd}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_equivalent_rank}}
			\end{maxi!}

			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{M-Boyd2004}, thus strong duality holds. The corresponding Lagrangian function at iteration $i$ is given by

@@

					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
				\end{equation}
			\end{subequations}
			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as

@@

				\Biggr)\nonumber\\
				&\quad- \mathrm{diag}(\boldsymbol{\nu^\star}).
			\end{align}
			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$. By reusing the proof in Appendix A of \cite{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$. On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$. Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} satisfies $\mathrm{rank}(\boldsymbol{\Phi}^\star)=1$. Due to the equivalence between \eqref{M-ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{M-op:irs}. We have clarified this point in Proposition~\ref{M-pr:relaxation}.

@@

		\begin{point}
			The figures in the current version are relatively small, it is suggested to provide larger figures to help the readers better understand the results.
			\label{pt:1.4}
		\end{point}

		\begin{response}
			We sincerely apologize for the inconvenience. The figures have been amplified in the revised manuscript.
			\label{re:1.4}
		\end{response}

		\begin{point}
			In the current version, the authors claimed that by applying semidefinite relaxation and omitting the rank-one constraint, the performance loss is negligible. The reviewer wonders if this is because of the relatively simple system model, as there is only one single user who has both power and information requirements. It could be better if the authors can further discuss this issue for a more general multiple user scenario.
			\label{pt:1.5}
		\end{point}

		\begin{response}
			We agree with the reviewer that the relaxation on the rank-one constraint deserves more attention. However, as discussed in Response~\ref{re:1.2}, multi-user IRS-aided SWIPT is out the scope of this paper and we would like to provide some general ideas to address this issue. For any passive beamforming problem with non-convex unit-rank constraint, if the proof to Proposition~\ref{M-pr:relaxation} is unavailable, existing approaches include 1) relax the constraint and use Gaussian randomization method to obtain a high-quality solution \cite{M-Luo2010}, 2) replace the unit-rank constraint with the constraint on largest singular value $\mathrm{Tr}(\boldsymbol{\Phi})-\sigma_{\max} (\boldsymbol{\Phi}) \le 0$ then solve the problem by the penalty method \cite{M-Wu2020a}, \cite{Wu2021}, 3) apply the gradient descent in the manifold space \cite{Zuo2020}. All three techniques are expected to provide a unit-rank solution with performance very close to the original solution.
			\label{re:1.5}
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			New RIS models are now being adopted as in \cite{M-Abeywickrama2019} where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
			\label{pt:2.1}
		\end{point}

@@

		\begin{response}
			Thank you for sharing this paper. It investigated the impact of non-zero effective resistance on the reflection pattern and pointed out that the amplitude of the reflection coefficient depends on the phase shift forced on the incoming signal when power dissipation is considered at the IRS. It also proposed an analytical IRS model together with an BCD algorithm to maximize the achievable rate by passive beamforming. Simulation results emphasized the importance of modeling such a relationship in practical IRS design. There exist various refined models of IRS in the literature, however, we have finally decided to use the most common and simplest IRS model at the current stage to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.
			\label{re:2.1}
		\end{response}

		\begin{point}
			Why is MRT considered as precoder by \eqref{M-eq:b_n} rather than optimizing it? Is it globally optimal too?
			\label{pt:2.2}
		\end{point}

@@

		\begin{response}
			In the single-user scenario, the global optimal information and power precoders coincide at MRT. To prove this, we decouple the waveform in the spatial and frequency domains by
			\begin{equation}\label{eq:w}
				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n}
			\end{equation}
			where $s_{\mathrm{I/P},n}$ denotes the amplitude of modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the information/power precoder. The MRT precoder at subband $n$ is given by
			\begin{equation}\label{eq:b}
				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}
			\end{equation}

			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate (8). From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{M-eq:y_I2}--\eqref{M-eq:y_P4}. Hence, MRT is the global optimal active precoder and no dedicated energy beams are required in the single-user SWIPT. We have separated the active beamforming design from the waveform design in the revised manuscript, summarized the conclusion in Proposition~\ref{M-pr:mrt}, and add the proof above to clarify this point.
			\label{re:2.2}
		\end{response}

@@

		\begin{point}
			Some strong assumptions like perfect CSI availability limit the practical utility of the proposed analytical results.
			\label{pt:2.3}
		\end{point}

		\begin{response}
			The reviewer is referred to Response \ref{re:1.1}. Indeed, the assumption of perfect CSIT is very ideal and the existing channel estimation protocols may not provide decent results in practice. We have investigated the impact of CSIT estimation error of the cascaded link on the R-E performance, and Fig.~\ref{fi:re_csi} shows that the proposed algorithms are robust to CSIT inaccuracy for different $L$.
			\label{re:2.3}
		\end{response}

		\begin{point}
			All the assumptions and relaxations adopted used in the derivation of results as in \eqref{M-eq:z_irs_approx} need to be explicitly mentioned along with appropriate justification for the same.
			\label{pt:2.4}
		\end{point}

		\begin{response}
			We appreciate your suggestion and have revised the manuscript correspondingly. The original objective function \eqref{M-eq:z_irs} is differentiable and non-concave in $\mathbb{C}^{4N - 2}$, and we approximate (linearize) the second-order terms by the first-order Taylor expansions \eqref{M-eq:taylor_1}--\eqref{M-eq:taylor_3} to formulate SCA problems of the original passive beamforming problem (i.e. maximize \eqref{M-eq:z_irs} s.t. \eqref{M-co:irs_rate}--\eqref{M-co:irs_rank}). Also, \eqref{M-eq:coupled_terms} holds due to symmetrical summation. Hence, the quadratic objective function \eqref{M-eq:z_irs_approx} is obtained by plugging \eqref{M-eq:taylor_1}--\eqref{M-eq:coupled_terms} into \eqref{M-eq:z_irs}. Solving relaxed problem \eqref{M-op:irs} iteratively is guaranteed to converge to a local optimal point of the original passive beamforming problem, and the proof is provided in Appendix~\ref{M-ap:sca}.
			\label{re:2.4}
		\end{response}

@@

		\begin{point}
			Some transformations have been made while solving the original problem, but it has not been explicitly mentioned whether it is equivalent to transformation or not.
			\label{pt:2.5}
		\end{point}

		\begin{response}
			Thank you for the reminder. All transformations are equivalent to their original form and we have mentioned this point explicitly in the revised manuscript.
			\label{re:2.5}
		\end{response}

		\begin{point}
			Are the proposed solutions locally optimal or globally optimal? It is not clear whether the convergence of proposed solution methodologies is local or global? Also, how fast is it?
			\label{pt:2.6}
		\end{point}

		\begin{response}
			Algorithm~\ref{M-al:sca}--\ref{M-al:lc_bcd} provide local optimal solutions with local convergence proof, and the performance indeed depends on the initialization. For the passive beamforming Algorithm~\ref{M-al:sca} and \ref{M-al:m_sca}, we initialize the phase shift of all IRS elements as i.i.d. uniform random variables over $[0, 2\pi)$. For Algorithm~\ref{M-al:gp}, we initialize the modulated waveform by the Water-Filling (WF) strategy \ref{eq:wf} and the multisine waveform by the Scaled Matched Filter (SMF) scheme \ref{eq:smf}, and assume $\rho^{(0)}=\bar{\rho}^{(0)}=1$. These parameters are used for general initialization and regulated automatically afterwards. However, as Algorithm~\ref{M-al:bcd} and \ref{M-al:lc_bcd} only converge to local optimal solutions, few R-E points might be strictly worse (with less rate and energy) than the others especially when $N$ is very large. To address this issue, we draw the R-E boundary from the high-rate low-energy (lower right) points to the low-rate high-energy (upper left) points. If a point is strictly dominated, we discard the candidate, reinitialize Algorithm~\ref{M-al:bcd} and \ref{M-al:lc_bcd} by the solution at the previous point, then perform the optimization again. For a tolerance of $\epsilon=10^{-8}$, Algorithm~\ref{M-al:sca}--\ref{M-al:lc_bcd} typically converge within 2, 7, 3, 2, 3 iterations, respectively.

@@

			We also would like to point out that, even in the absence of IRS, the problem of joint waveform and beamforming design for SWIPT is also non-convex and algorithms only converging toward a local optimum have been identified, with the global optimum remaining unsolved.
			\label{re:2.6}
		\end{response}

### 2021-04-24 main.tex
:pencil: Update manuscript

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength. To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency. This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS. Considering energy harvester nonlinearity and practical transceiving strategies, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT). This non-convex problem is then solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is retrieved by the Geometric Programming (GP) technique. Since the computational complexity of the GP algorithm scales exponentially with the number of subbands, we also propose two closed-form adaptive waveform schemes to facilitate practical SWIPT implementation. Simulation results demonstrate that the proposed algorithms bring considerable R-E gains and are robust to CSIT inaccuracy and finite IRS reflection states. Results also emphasize the importance of accounting harvester nonlinearity in the passive beamforming design.
	\end{abstract}

@@

            The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. \cite{Zhou2013} proposed two practical co-localized information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS). Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape. It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then performed joint waveform and beamforming design for WPT. Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}. A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage is then demonstrated in a prototype with channel acquisition \cite{Kim2017}. Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
		\end{subsection}

@@

		\begin{subsection}{IRS-Aided SWIPT}
			Both SWIPT and IRS aim to achieve spectrum- and energy-efficient transmission, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT. For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links could boost the WSP because rank-deficient channels tend to require fewer energy beams. However, \cite{Wu2020b,Tang2019,Wu2020a} only consider single-carrier transmission based on an inaccurate linear energy harvester model. Motivated by this, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS in this paper. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.

@@

			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation. To accommodate the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS. The proposed low-complexity designs achieve near-optimal R-E performance under different configurations.

@@

			\emph{Organization:} Section~\ref{se:system_model} introduces the system model, transceiving modes, rectifier nonlinearity and R-E tradeoff. Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming optimization. Section~\ref{se:performance_evaluation} evaluates the proposed algorithms by simulation results. Section~\ref{se:conclusion_and_future_works} concludes the paper.

@@

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands. We consider a quasi-static block fading model and assume the CSIT of AP-UE direct channel and AP-IRS-UE cascaded channel are known. The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.

@@

		\begin{subsection}{Reflection Pattern and Composite Channel}
			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances. IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and its reflection coefficient is defined as
			\begin{equation}
				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l}
			\end{equation}
			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$. This paper sticks to the commonest and simplest IRS model where the reflection amplitude is always assumed unit to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift. We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.

			\begin{remark}\label{re:reflection_coefficient}
				The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely. Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands. In this paper, we assume the bandwidth is incomparable to the operating frequency such that the reflection coefficient of each IRS element is the same at all subbands.
			\end{remark}

>>>>

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength. To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency. This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS. Considering energy harvester nonlinearity and practical receiving modes, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT). This non-convex problem is solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is retrieved by the Geometric Programming (GP) technique. Since the computational complexity of the GP algorithm scales exponentially with the number of carriers, we also propose two closed-form adaptive waveform schemes to facilitate practical SWIPT implementation. Simulation results demonstrate that the proposed algorithms bring considerable R-E gains and are robust to CSIT inaccuracy and finite IRS reflection states. Results also emphasize the importance of accounting harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
	\end{abstract}

@@

            The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. \cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS). Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape. It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then performed joint waveform and beamforming design for WPT. Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}. A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage is then demonstrated in a prototype with channel acquisition \cite{Kim2017}. Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
		\end{subsection}

@@

		\begin{subsection}{IRS-Aided SWIPT}
			Both SWIPT and IRS aim to achieve spectrum- and energy-efficient transmission, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT. For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links could boost the WSP because rank-deficient channels tend to require fewer energy beams. However, \cite{Wu2020b,Tang2019,Wu2020a} only consider single-carrier transmission based on an inaccurate linear energy harvester model. Unfortunately, such modeling is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}. In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.

@@

			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation. To accommodate the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the combining and splitting ratios for PS. The proposed low-complexity designs achieve near-optimal R-E performance under different configurations.

@@

			\emph{Organization:} Section~\ref{se:system_model} introduces the system model, receiving modes, rectifier nonlinearity and R-E tradeoff. Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming optimization. Section~\ref{se:performance_evaluation} evaluates the proposed algorithms by simulation results. Section~\ref{se:conclusion_and_future_works} concludes the paper.

@@

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands. We consider a quasi-static block fading model and assume the CSIT of direct and cascaded channels are known. The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.

@@

		\begin{subsection}{Reflection Pattern and Composite Channel}
			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances. IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and its reflection coefficient is defined as
			\begin{equation}
				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l}
			\end{equation}
			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$. This paper sticks to the most common and simplest IRS model where the reflection amplitude is always assumed equal to \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift. We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.

			\begin{remark}\label{re:reflection_coefficient}
				The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely. Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands. In this paper, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each IRS element is the same at all subbands.
			\end{remark}
